---
title: "Web APIs"
author: Anil Akyildirim
date: "10/19/2019"
output:
  html_document:
    code_download: yes
    code_folding: hide
    highlight: pygments
    number_sections: yes
    theme: flatly
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r}
#load libraries

library(httr)
library(jsonlite)
library(dplyr)
library(ggplot2)

```


# Introduction

In this assignment, we are tasked to create an developer account within The New York Times website APIs, similarly describe here: https://developer.nytimes.com/apis and further read the information within the JSON data that the API provides and create a dataframe for future analysis. In order to do this, we select one of the Publicly available API's listed in the New York times API Catalog. I have selected Most Popular API and further created an app with an ID and an API Key.

# About the Data

The Most Popular API provides a service getting the most popular articles on NYtimes.com based on emails, shares or views. In this case, I wanted to look at the most shared nytimes articles via facbook for the last 7 days. Based on the documentation provided in the developer guide, my api call should look something like this: " https://api.nytimes.com/svc/mostpopular/v2/shared/7/facebook.json " 

# Data Collection


```{r}

url <- "https://api.nytimes.com/svc/mostpopular/v2/shared/7/facebook.json"
api_key <- "qGvyiL1P77XmJvdGxUu4vufM462qN59H"

#update the url with api key structure example: https://api.nytimes.com/svc/mostpopular/v2/shared/1/facebook.json?api-key=yourkey 

url <- paste(url, "?", "api-key=", api_key, sep = "")
fb_shares <- GET(url, verbose())
fb_shares

```

## Creating the Data Frame

```{r}
#set content and read it from JSON
content <- content(fb_shares, "text")
fb_shares <- fromJSON(content)

#create the dataframe
fb_shares <- as.data.frame(fb_shares)
fb_shares
```

# Data Preperation

```{r}
# select the columns that we think will help with analysis.

fb_shares <- select(fb_shares, results.subsection, results.share_count, results.section, results.type)
colnames(fb_shares) <- c("sub_section", "share_count", "section", "type")
head(fb_shares)
str(fb_shares)

```

# Data Exploration and Conclusion

```{r}
theme_set(theme_classic())

ggplot(fb_shares, aes(type, share_count))+
  geom_bar(stat="identity", width = 0.5, fill="tomato2")+
  theme(axis.text.x=element_text(angle=65, vjust=0.6))


```

```{r}
theme_set(theme_classic())

ggplot(fb_shares, aes(sub_section, share_count))+
  geom_bar(stat="identity", width = 0.5, fill="tomato2")+
  theme(axis.text.x=element_text(angle=65, vjust=0.6))


```

We have 20 observations from ny times articles that are shared within the last 7 days in facebook. Not including the blank values under the sub section, we see that political articles are shared the most within the facebook users the most, for the last 7 days. 



